Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-08 paper/paper.tex

In order to determine the validity of the {\sc synth} formula, we can now
check the {\sc synth} program for safety.  The {\sc synth} program is a
\newC program, which means we can check its safety by invoking a bounded
model checker, such as {\sc cbmc}.  Since \newC is a fragment of C,
the {\sc synth} program can also be compiled using {\sc gcc}.
We can add a small piece of code which enumerates each possible
$\mathcal{L}$-programs, then evaluates program on the current test vectors by
running {\sc synth}. If it finds a program which is correct, it emits
the program as a candidate, just like a conventional superoptimiser.
The combination of this enumeration function and {\sc synth} can be compiled
to an executable using {\sc gcc}.  This leaves
us with a very simple explicit-state model checker which decides
safety for {\sc synth}.  We can run the explicit-state model checker
in parallel with {\sc cbmc} and take the answer of whichever happens
to terminate first, stopping the other process.  This procedure is
depicted for {\sc synth} in Fig.~\ref{fig:synth-dfd} and for
{\sc verif} in Fig.~\ref{fig:verif-dfd}.

@@

@@

@@

>>>>

In order to determine the validity of the {\sc synth} formula, we can now
check the {\sc synth} program for safety.  The {\sc synth} program is a
\newC program, which means we can check its safety by invoking a bounded
model checker, such as {\sc cbmc}.  Since \newC is a fragment of C,
the {\sc synth} program can also be compiled using {\sc gcc}.
We can add a small piece of code which enumerates each possible
$\mathcal{L}$-program, then evaluates each program on the current test vectors by
running {\sc synth}. If it finds a program which is correct, it emits
the program as a candidate, just like a conventional superoptimiser.
The combination of this enumeration function and {\sc synth} can be compiled
to an executable using {\sc gcc}.  This leaves
us with a very simple explicit-state model checker which decides
safety for {\sc synth}.  We can run the explicit-state model checker
in parallel with {\sc cbmc} and take the answer of whichever happens
to terminate first, stopping the other process.  This procedure is
depicted for {\sc synth} in Fig.~\ref{fig:synth-dfd} and for
{\sc verif} in Fig.~\ref{fig:verif-dfd}.

@@

TODO
Explain parameterisations of L
Explain how we search through the parameters

@@

TODO
Explain 2sum

@@

TODO
Explain experiments
Explain difference to Brahma (to explain timeouts)
Run experiments on Sketch and AHA
